Waveform and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer

### 2020-07-10 main.tex
:pencil: Outer loop algorithm

	\begin{subsection}{Objective and Methodology}
		In this paper, we study an IRS-aided multiuser Single-Input Single-Output (SISO) system where the IRS assists the information and energy transmission of all users. A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g. OFDM) to boost the energy transfer efficiency with no interference. The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff. Different from previous research, this paper investigates the fundamental impact of harvester nonlinearity on waveform and IRS design. We transform the R-E region characterization problem into multiple current maximization problems subject to different rate constraints. To reduce the design complexity, we	propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semi-Definite Relaxation (SDR) technique. It was observed that dedicated power waveform boosts the energy transmission efficiency such that TS and PS are preferred for low-rate and high-rate applications respectively. Also, FF-IRS produces a significant channel amplification and R-E enhancement especially when developed near the transmitter, and the performance loss compared with ideal Frequency-Selective (FS) IRS decreases as the number of reflectors increases.
	\end{subsection}
\end{section}

\begin{section}{System Model}
	Consider an IRS-aided multiuser MISO OFDM SWIPT system where the $M$-antenna transmitter delivers information and power simultaneously, through a single $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands. We assume a total bandwidth $B$ with evenly-spaced carriers around center frequency $f_c$. Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$). Each subband is allocated to one user per time slot. Perfect Channel State Information (CSI) with negligible training overhead is considered to explore the analytical upper-bound of the proposed design. A quasi-static block fading channel model is considered for all links and we focus on one particular block where the channels are approximately unchanged. We characterize and compare the R-E region achieved by TS and PS receivers. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into data and energy streams for ID and EH purposes, and the splitting ratio $\rho$ is coupled with waveform and IRS design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
	\begin{subsection}{Transmit Signal}
		Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which belongs to one user at time $t$ and follows a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$. Let $\alpha_{k,n}$ be the allocation indicator, namely if subband $n$ is given to user $k$ ($k=1,\dots,K$), we have $\alpha_{k,n}=1$ and $\alpha_{k',n}=0 \ \forall k' \ne k$. Let $\boldsymbol{\alpha}_k=[\alpha_{k,1},\dots,\alpha_{k,N}]^T \in \mathbb{C}^{N \times 1}$. The superposed transmit signal at time $t$ on antenna $m$ ($m=1,\dots,M$) is
		\begin{equation}\label{eq:x_m}
			x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n,m}\tilde{x}_{I,n}(t)}+w_{P,n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
		\end{equation}
		where $w_{I/P,n,m}=s_{I/P,n,m}e^{j\psi_{I/P,n,m}}$ denotes the weight on the information and power signal transmitted by antenna $m$ at subband $n$. We further define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$ such that the transmit information and power signals write as
		\begin{align}
			\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_I}\\
			\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_P}
		\end{align}
	\end{subsection}

	\begin{subsection}{Composite Channel}
		At subband $n$, denote the AP-user $k$ direct channel as $\boldsymbol{h}_{D,k,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and the IRS-user $k$ reflective channel as $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. On top of this, the IRS matrix collects the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user channel. Hence, the composite channel for user $k$ over subband $n$ is
		\begin{equation}\label{eq:h_{k,n}}
			\boldsymbol{h}_{k,n}^H = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{h}_{R,k,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{k,n}
		\end{equation}
		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{k,n}=\mathrm{diag}(\boldsymbol{h}_{R,k,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Let $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$ and $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1}^T,\dots,\boldsymbol{V}_{k,N}^T]^T \in \mathbb{C}^{L \times MN}$. Also, define $\boldsymbol{A}_{k,n}=\lvert \boldsymbol{h}_{k,n} \rvert$ and $\boldsymbol{\varsigma}_{k,n}=\angle{\boldsymbol{h}_{k,n}}$ as the magnitude and phase of the composite channel for user $k$ over subband $n$.
	\end{subsection}

@@

	\begin{subsection}{Information Decoder}
		A major benefit of the proposed waveform is that the power component $y_{P,k}(t)$ creates no interference to the information component $y_{I,k}(t)$. Hence, the achievable rate of user $k$ is
		\begin{equation}\label{eq:R_k}
			R_k(\boldsymbol{w}_I,\boldsymbol{\phi},\rho,\boldsymbol{\alpha}_k)=\sum_{n=1}^N\alpha_{k,n}{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
		\end{equation}
		where $\sigma_n^2$ is the variance of the noise at RF band and during RF-to-BB conversion on tone $n$. Rate \ref{eq:R_k} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
	\end{subsection}

	\begin{subsection}{Energy Harvester}
		Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2016a,Clerckx2018b}, which highlights the dependency of harvester output DC current on the received waveform of user $k$ as
		\begin{equation}\label{eq:i_k}
			i_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
		\end{equation}
		where $R_{\text{ant}}$ is the impedance of the receive antenna, $k_0'=i_s(e^{-i_kR_{\text{ant}}/nv_t}-1)$, $k_i'=i_se^{-i_kR_{\text{ant}}/nv_t}/i!(nv_t)^i$ for $i=1,\dots,\infty$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage. For a fixed channel and waveform, $\mathcal{A}\left\{.\right\}$ extracts the DC component of the received signal while $\mathcal{E}\left\{.\right\}$ covers the expectation over $\tilde{x}_{I,n}$.

@@

	\begin{subsection}{Weighted Sum Rate-Energy Region}
		Define the achievable weighted sum R-E region as
		\begin{equation}
			\begin{split}
				C_{R-I}(P)
				&\triangleq \biggl\{(R,Z):R\le\sum_{k=1}^K{u_{I,k}R_k},Z\le\sum_{k=1}^K u_{P,k}z_k,\\
				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}) \le P\biggr\}
			\end{split}
		\end{equation}
		where $P$ is the transmit power budget and $u_{I,k},u_{P,k}$ are the information and power weight of user $k$.
	\end{subsection}
\end{section}

\begin{section}{Single-User Optimization}
	Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$. We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
	\begin{maxi!}
		{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{\label{eq:su_target}}
		\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
		\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraint}
		\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
		\addConstraint{0 \le \rho \le 1}
	\end{maxi!}
	Problem \ref{op:su} is intricate due to the non-convex objective function \ref{eq:su_target} and constraint \ref{eq:su_rate_constraint} with coupled variables. To reduce the design complexity, we propose an suboptimal AO algorithm that updates the IRS phase shift, transmit waveform, and receive splitting ratio iteratively.

	\begin{subsection}{IRS Phase Shift}
		\begin{subsubsection}{Frequency-Selective IRS}\label{se:fs_irs}
			In the ideal case, each element in FS-IRS is expected to provide subband-dependent reflection coefficients. Hence, $\boldsymbol{\phi}_n$ replaces $\boldsymbol{\phi}$ in \ref{op:su} and the IRS has a total Degree of Freedom (DoF) of $NL$. Note that $\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{v}_n^H\boldsymbol{\phi}_n w_{I,n}}\rvert$ where the equality holds when the direct and IRS-aided links are aligned. Therefore, we simply select the phase shift of element $l$ at subband $n$ as
			\begin{equation}\label{eq:theta}
				\theta_{n,l}^\star = \angle{h}_{D,n} - \angle{h_{R,n,l}}-\angle{h_{I,n,l}}
			\end{equation}
			That is to say, the optimal phase shift is obtained in closed form in the single-user scenario, which ensures the direct, extra and composite channels have the same phase.
		\end{subsubsection}

		\begin{subsubsection}{Frequency-Flat IRS}
			In contrast, FF-IRS reflects all subbands equally with a DoF of $L$. We observe that

@@

			with $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Similarly, we have

@@

			We then introduce auxiliary variables

@@

			with $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as

@@

				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}

@@

			We then relax the rank constraint \ref{co:irs_rank} and solve the optimal IRS matrix $\boldsymbol{\Phi}^{\star}$ iteratively by interior-point method. If $\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is attained by eigenvalue decomposition (EVD). Otherwise, a best feasible candidate $\bar{\boldsymbol{\phi}}^\star$ can be extracted through Gaussian randomization method \cite{Huang2010}. We first perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$. Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$. Next, the optimal solution $\bar{\boldsymbol{\phi}}^\star$ is approximated by the one maximizes the objective function \ref{eq:su_irs_target}. Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$. The algorithm for the phase shift optimization subproblem is summarized in Algorithm \ref{al:ff_irs}.

@@

				\caption{FF-IRS: Phase Shift}

@@

					\State Construct $\boldsymbol{M},\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:M}, \ref{eq:R_n,phi}, \ref{eq:C_{I/P,n}}

@@

					\State Select the best solution $\boldsymbol{\Phi}^\star$ and $\boldsymbol{\phi}^\star$ for problem \ref{op:su_irs}

@@

				\psi_{I,n}^{\star}=\psi_{P,n}^{\star}=-\bar{\psi}_{n}

@@

				\lvert{(h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}_n)w_{I,n}}\rvert = \lvert h_{D,n} \rvert \lvert w_{I,n} \rvert + \vert \boldsymbol{v}_n^H\boldsymbol{\phi}_n \rvert \lvert w_{I,n} \rvert

@@

			Also, denote the waveform amplitude at subband $n$ as
			\begin{equation}\label{eq:s}
				s_{I/P,n} = \lvert w_{I/P,n} \rvert
			which is further collected into $\boldsymbol{s}_{I/P} \in \mathbb{C}^{N \times 1}$. Therefore, the original problem \ref{op:su} is reduced to an amplitude optimization problem

@@

					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)} \ge \bar{R}}

@@

						&=\frac{1}{2}{\beta_2}{\rho}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}\\
						&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(\left(\sum_{n}(A_n s_{I,n})^2\right)^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\right)\\
						&\quad+\frac{3}{2}{\beta_4}{\rho^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}

@@

			with $z$ given by \ref{eq:z_gp}. We introduce an auxiliary variable $t''$ and transform problem \ref{op:su_gp} into

@@

					\State Retrieve channel amplitude response $A_n \ \forall n$ by \ref{eq:h_{k,n}}

>>>>

	\begin{subsection}{Objective and Methodology}
		In this paper, we study an IRS-aided multiuser MISO SWIPT system where the IRS assists the information and energy transmission of all users. A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g. OFDM) to boost the energy transfer efficiency without introducing additional interference. The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff. Different from previous research, this paper investigates the fundamental impact of harvester nonlinearity on waveform and IRS design. We transform the R-E region characterization problem into multiple current maximization problems subject to different rate constraints. To reduce the design complexity, we	propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semi-Definite Relaxation (SDR) technique. It was demonstrated that dedicated power waveform boosts the energy transmission efficiency such that TS and PS are preferred for low-rate and high-rate applications respectively. Also, IRS brings a significant channel amplification and R-E enhancement especially when located near the transmitter, and the performance loss compared with ideal Frequency-Selective (FS) IRS decreases as the number of reflectors increases.
	\end{subsection}
\end{section}

\begin{section}{System Model}
	Consider an IRS-aided multiuser MISO OFDM SWIPT system where the $M$-antenna transmitter delivers information and power simultaneously, through a single $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands. We assume a total bandwidth $B$ with evenly-spaced subbands around center frequency $f_c$. Each subband is allocated to one user per time slot, and denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$). Perfect Channel State Information (CSI) with negligible training overhead is assumed to explore the analytical upper-bound of the proposed design. A quasi-static block fading channel model is considered for all links and we focus on one particular block where the channels are approximately unchanged. We characterize and compare the R-E region achieved by TS and PS receivers. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into data and energy streams for ID and EH, and the splitting ratio $\rho$ is coupled with waveform and IRS design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted.
	\begin{subsection}{Transmit Signal}
		Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which belongs to one user at time $t$ and follows a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$. Let $\alpha_{k,n}$ be the allocation indicator, namely if subband $n$ is given to user $k$ ($k=1,\dots,K$), we have $\alpha_{k,n}=1$ and $\alpha_{k',n}=0$ for $k' \ne k$. Let $\boldsymbol{\alpha}_k=[\alpha_{k,1},\dots,\alpha_{k,N}]^T \in \mathbb{C}^{N \times 1}$. The superposed transmit signal at time $t$ on antenna $m$ ($m=1,\dots,M$) is
		\begin{equation}\label{eq:x_m}
			x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n,m}\tilde{x}_{I,n}(t)}+w_{P,n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
		\end{equation}
		where $w_{I/P,n,m}=s_{I/P,n,m}e^{j\psi_{I/P,n,m}}$ denotes the weight on the information and power signal transmitted by antenna $m$ at subband $n$. Let $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ such that the transmit information and power signals write as
		\begin{align}
			\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_I}\\
			\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\label{eq:x_P}
		\end{align}
		We also define $\boldsymbol{w}_{I/P}=[\boldsymbol{w}_{I/P,1}^T,\dots,\boldsymbol{w}_{I/P,N}^T]^T \in \mathbb{C}^{MN \times 1}$ and let $\boldsymbol{s}_{I/P}=\lvert{\boldsymbol{w}_{I/P}}\rvert$, $\boldsymbol{\psi}_{I/P}=\angle{\boldsymbol{w}_{I/P}}$ be the magnitude and phase of the waveforms.
	\end{subsection}

	\begin{subsection}{Composite Channel}
		At subband $n$, denote the AP-user $k$ direct channel as $\boldsymbol{h}_{D,k,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user $k$ reflective channel as $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. On top of this, the IRS matrix collects the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user channel. Hence, the composite channel for user $k$ over subband $n$ is
		\begin{equation}\label{eq:h_{k,n}}
			\boldsymbol{h}_{k,n}^H = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{h}_{R,k,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,k,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{k,n}
		\end{equation}
		where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{k,n}=\mathrm{diag}(\boldsymbol{h}_{R,k,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Similarly, we define $\boldsymbol{h}_k=[\boldsymbol{h}_{k,1}^T,\dots,\boldsymbol{h}_{k,N}^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{V}_k=[\boldsymbol{V}_{k,1}^T,\dots,\boldsymbol{V}_{k,N}^T]^T \in \mathbb{C}^{L \times MN}$ and let $\boldsymbol{a}_{k}=\lvert \boldsymbol{h}_{k} \rvert$, $\boldsymbol{\varsigma}_{k}=\angle{\boldsymbol{h}_{k}}$ be the magnitude and phase of the composite channel for user $k$.
	\end{subsection}

@@

	\begin{subsection}{Information Decoder}
		A major benefit of the proposed waveform is that the power component $y_{P,k}(t)$ creates no interference to the information component $y_{I,k}(t)$. Hence, the achievable rate of user $k$ is
		\begin{equation}\label{eq:R_k}
			R_k(\boldsymbol{w}_I,\boldsymbol{\phi},\rho,\boldsymbol{\alpha}_k)=\sum_{n=1}^N\alpha_{k,n}{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{k,n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
		\end{equation}
		where $\sigma_n^2$ is the variance of the noise at RF band and during RF-to-BB conversion on tone $n$. Rate \ref{eq:R_k} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
	\end{subsection}

	\begin{subsection}{Energy Harvester}
		Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2016a,Clerckx2018b}, which highlights for user $k$ the dependency of harvester output DC current on the received waveform as
		\begin{equation}\label{eq:i_k}
			i_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
		\end{equation}
		where $R_{\text{ant}}$ is the impedance of the receive antenna, $k_0'=i_s(e^{-i_kR_{\text{ant}}/nv_t}-1)$, $k_i'=i_se^{-i_kR_{\text{ant}}/nv_t}/i!(nv_t)^i$ for $i=1,\dots,\infty$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage. For a fixed channel and waveform, $\mathcal{A}\left\{.\right\}$ extracts the DC component of the received signal while $\mathcal{E}\left\{.\right\}$ covers the expectation over $\tilde{x}_{I,n}$.

@@

	\begin{subsection}{Weighted Sum Rate-Energy Region}
		Define the achievable weighted sum R-E region as
		\begin{equation}
			\begin{split}
				C_{R-Z}(P)
				&\triangleq \biggl\{(R,Z):R\le\sum_{k=1}^K{u_{I,k}R_k},Z\le\sum_{k=1}^K u_{P,k}z_k,\\
				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}) \le P\biggr\}
			\end{split}
		\end{equation}
		where $P$ is the transmit power budget and $u_{I,k},u_{P,k}$ are the information and power weight of user $k$.
	\end{subsection}
\end{section}

\begin{section}{Single-User Optimization}
	Consider a single-user waveform and IRS optimization problem where $\boldsymbol{\alpha}=\boldsymbol{1}^{N \times 1}$. We characterize the rate-energy region through a current maximization problem subject to transmit power, rate, and IRS constraints
	\begin{maxi!}
		{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho}{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\phi},\rho)}{\label{op:su}}{\label{eq:su_target}}
		\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
		\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(\boldsymbol{h}_{D,n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}\label{eq:su_rate_constraint}
		\addConstraint{\lvert{\phi}\rvert=1, \quad l=1,\dots,L}
		\addConstraint{0 \le \rho \le 1}
	\end{maxi!}
	Problem \ref{op:su} is intricate due to coupled variables and non-convex objective function \ref{eq:su_target} and constraint \ref{eq:su_rate_constraint}. To reduce the design complexity, we propose an suboptimal AO algorithm that updates the IRS phase shift, transmit waveform, and receive splitting ratio iteratively.

	\begin{subsection}{IRS Phase Shift}
		We optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{I/P,n}$ and splitting ratio $\rho$. Since

@@

		with
		\begin{equation}\label{eq:C_n}
			\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{I,n}\boldsymbol{w}_{I,n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}
		Similarly, we have

@@

		Next, introduce auxiliary variables

@@

		with
		\begin{equation}\label{eq:C_{I/P,n}}
			\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}
		Therefore, \ref{eq:z_k_channel} rewrites as

@@

				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}

@@

		We then relax the rank constraint \ref{co:irs_rank} and solve the optimal IRS matrix $\boldsymbol{\Phi}^{\star}$ iteratively by interior-point method. If $\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is attained by eigenvalue decomposition (EVD). Otherwise, a solution can be extracted through Gaussian randomization method \cite{Huang2010}. We first perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$. Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates by
			\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}
		The candidate maximizing the objective function \ref{eq:su_irs_target} is chosen as the optimal solution $\bar{\boldsymbol{\phi}}^\star$. Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$. The algorithm for the phase shift optimization is summarized in Algorithm \ref{al:ff_irs}.

@@

			\caption{IRS Phase Shift}

@@

				\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{I/P,n} \ \forall n$ by \ref{eq:M}, \ref{eq:M_n,phi}, \ref{eq:C_n}, \ref{eq:C_{I/P,n}}
				\Repeat;

@@

				\State Select the best solution $\boldsymbol{\Phi}^\star$ and $\bar{\boldsymbol{\phi}}^\star$ for problem \ref{op:su_irs}

@@

				\boldsymbol{\psi}_{I}^{\star}=\boldsymbol{\psi}_{P}^{\star}=-\boldsymbol{\varsigma}

@@

				\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert^2=(\boldsymbol{a}_n^H\boldsymbol{s}_{I,n})^2=\sum_{m_1,m_2}\prod_{j=1}^2{a_{n,m}s_{I,n,m}} \triangleq E_n

@@

			Therefore, the original problem \ref{op:su} is reduced to an amplitude optimization problem

@@

					\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho)E_n}{\sigma_n^2}\right)} \ge \bar{R}}

@@

						& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \sum_{m_1,m_2} \left( \prod_{j=1}^2 {a_{n,m_j}s_{I,n,m_j}} + \prod_{j=1}^2 {a_{n,m_j}s_{P,n,m_j}} \right)\\
						& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n_1,m_j}s_{I,n_1,m_j} \prod_{j=2,4} a_{n_2,m_j}s_{I,n_2,m_j} + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1}^4 a_{n_j,m_j}s_{P,n_j,m_j} \right)\\
						& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \sum_{m_1,m_2,m_3,m_4} \prod_{j=1,3} a_{n,m_j}s_{I,n,m_j} \prod_{j=2,4} a_{n,m_j}s_{P,n,m_j} \right)

@@

			with $z$ expressed in \ref{eq:z_gp}. We introduce an auxiliary variable $t''$ and rewrite problem \ref{op:su_gp} as

@@

					\State Retrieve channel magnitude and phase $\boldsymbol{a}, \varsigma$
